---
title: "Effectiveness analysis of Juntos Santiago cluster randomized trial"
author: "Sebastián Peña, Cristóbal Cuadrado, Pedro Zitko, Jukka Konto"
date: "18 December 2018"
output: html_document
---

## Introduction

This is the script for the analysis of effectiveness of the cluster randomized Juntos Santiago trial. Outcomes as registered in ClinicalTrials.gov (NCT03459742)

Primary outcome: Zscore
Secondary outcomes: BMI, waist circumference, systolic blood pressure, diastolic blood pressure

Individual level data: 
Sex, age, class, nationality, National School Food Programme (PAE) y/n, educational level of parents, o

School level data:
Number of students, proportion male/female, Index of School Vulnerability (only for public and private-subsidized schools), type of school (public, private subsidized and private) and type of Administrator (e.g. Municipal, Religious, Non-religious).


## Data management

The dataset has been read from Excel and data has been managed in Stata. The uploaded Stata dataset already has the variables labelled and correctly defined. But sometimes the import of Stata leads to  problems, such as factor variables not recognized as such.

```{r setup, include=FALSE}

```


## Exploratory data analysis

```{r setup, include=FALSE}


```


## Multilevel analysis to estimate mean difference at times T2 and T3

```{r}


```

## Marginal effects to produce estimated means at T1, T2 and T3


```{r}

```

## Graphs

```{r}

```
